---
title: "RWorksheet_Benedicto#2.R"
author: "Gabriel R. Benedicto"
date: "2024-09-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Using Vectors
** 1.Create a vector using : operator **
A. Sequence from -5 to 5. Write the R code and its output.
Describe its output. (The output is that it creates a sequence of integers between two values)
```{r}
x <- -5:5
x
```
B. x <- 1:7. What will be the value of x? (The Value of x will be 1 2 3 4 5 6 7)
```{r}
x <- 1:7
x
```
** 2. Create a vector using seq() function **
a. seq(1, 3, by=0.2) # specify step size
Write the R script and its output. Describe the output.
(The sequence starts at 1 and ends at 3, with each value incremented by 0.2)
```{r}
x <- seq(1, 3, by=0.2)
x
```
** 3. A factory has a census of its workers. There are 50 workers in total. The following
list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,
18. **
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 
          50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38, 41, 
          48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
ages
```

A. Access 3rd element, what is the value?(22)
```{r}
ages[3]
```
B. Access 2nd and 4th element, what are the values?(28 & 36)
```{r}
ages[c(2, 4)]
```
C. c. Access all but the 4th and 12th element is not
included. Write the R script and its output.
OUTPUT: [1] 34 28 22 27 18 52 39 42 29 35 27 22 37 34 19 20 57 49 50 37 46 25 17 37 43 53 41 51 35 
    24 33 41 53 40 18 44 38 41 48 27 39 19 30 61 54 58 26 18

```{r}
ages[-c(4, 12)]

```
**4. Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the
vector, names(x).**
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
x
```

A.Print the results. Then access x[c("first", "third")].
Describe the output.
  OUTPUT(first third
             3     9).
```{r}
x
x[c("first", "third")]

```
B.Write the code and its output. 
OUTPUT : 
first second  third 
     3      0      9 
first third 
    3     9 
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
x
x[c("first", "third")]

```
** 5. Create a sequence x from -3:2.**
```{r}
x <- -3:2
x
```

A.Modify 2nd element and change it to 0;
x[2] <- 0
x
Describe the output. ([1] -3  0 -1  0  1  2)
```{r}
x[2] = 0
x
```
B. Write the code and its output.
OUTPUT: ([1] -3  0 -1  0  1  2)
```{r}
x <- -3:2
x[2] <- 0
x
```
** 6. *The following data shows the diesel fuel purchased by Mr. Cruz.
Month Jan Feb March Apr May June
Price per liter (PhP) 52.50 57.25 60.00 65.00 74.25 54.00
Purchase–quantity(Liters) 25 30 40 50 10 45.
A.Create a data frame for month, price per liter (php), and purchase quantity (liters).
```{r}
month <- c("Jan", "Feb", "March", "Apr", "May", "June")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)

fuel_data <- data.frame(month, price_per_liter, purchase_quantity)

fuel_data

```
B.What is the average fuel expenditure of Mr. Cruz from
Jan to June? Note: Use ‘weighted.mean(liter,
purchase)‘. Write the R scripts and its output.
OUTPUT:  (59.2625)
```{r}
average_fuel_expenditure <- weighted.mean(price_per_liter, purchase_quantity)
average_fuel_expenditure
```
** 7. R has actually lots of built-in datasets. For example, the rivers data “gives the lengths
(in miles) of 141 “major” rivers in North America, as compiled by the US Geological
Survey”.**
a. Type “rivers” in your R console.
Create a vector data with 7
elements, containing the number of elements (length)
in rivers, their sum (sum), mean (mean),
median(median), variance(var), standard deviation(sd),
minimum (min) and maximum (max).
```{r}
data(rivers)

data <- c(
  length(rivers),        # Number of elements
  sum(rivers),           # Sum of all elements
  mean(rivers),          # Mean
  median(rivers),        # Median
  var(rivers),           # Variance
  sd(rivers),            # Standard deviation
  min(rivers),           # Minimum value
  max(rivers)            # Maximum value
)

data

```
B. What are the results?
Length: 141.0000
Sum: 83357.0000
Mean: 591.1844 
Median: 425.0000
Variance: 243908.4086
Standard:  493.8708
Minimum:  135.0000
Maximum: 3710.0000

C. Write the R scripts and its outputs.
OUTPUTS:
Length: 141.0000
Sum: 83357.0000
Mean: 591.1844 
Median: 425.0000
Variance: 243908.4086
Standard:  493.8708
Minimum:  135.0000
Maximum: 3710.0000
```{r}
data(rivers)

data <- c(
  length(rivers),        # Number of elements
  sum(rivers),           # Sum of all elements
  mean(rivers),          # Mean
  median(rivers),        # Median
  var(rivers),           # Variance
  sd(rivers),            # Standard deviation
  min(rivers),           # Minimum value
  max(rivers)            # Maximum value
)

data

```
** 8. **
A. Create vectors according to the above table.
Write the R scripts and its output.
```{r}
power_ranking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)
celebrity_name <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", 
                    "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", 
                    "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali", 
                    "Paul McCartney", "George Lucas", "Elton John", "David Letterman", 
                    "Phil Mickelson", "J.K Rowling", "Bradd Pitt", "Peter Jackson", 
                    "Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant")
pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)

power_ranking
celebrity_name
pay

```
B.Modify the power ranking and pay of J.K. Rowling.
Change power ranking to 15 and pay to 90. Write the
R scripts and its output.
```{r}
celebrity_name[19] <- "J.K Rowling"
power_ranking[19] <- 15
pay[19] <- 90

power_ranking
celebrity_name
pay

```
C. Create an excel file from the table above and save it
as csv file(PowerRanking). Import the csv file into
the RStudio. What is the R script?
```{r}
power_ranking_data <- read.csv("Powerranking.csv")

```
D.Access the rows 10 to 20 and save it as Ranks.RData.
Write the R script and its output.
```{r}
subset_data <- power_ranking_data[10:20, ]

save(subset_data, file = "Ranks.RData")

print(subset_data)

```
E. Describe its output.
The output table containing rows 10 to 20. This includes the celebrities ranked from 10th to 20th position, their names, and their corresponding pay, which is stored in the csv file.
** 9. Download the Hotels-Vienna https://tinyurl.com/Hotels-Vienna **
a. Import the excel file into your RStudio.
What is the R script?
```{r}
library(openxlsx)
hotels_vienna <- read.xlsx("hotels-vienna.xlsx")

```
B. How many dimensions does the dataset have?
What is the R script? WHat is its output? ([1] 428  24)
```{r}
dim(hotels_vienna)
```
C. Select columns country, neighbourhood,
price, stars, accomodation_type, and
ratings. Write the R script.
```{r}
selcol <- hotels_vienna[, c("country", "neighbourhood", "price", "stars", "accommodation_type", "rating")]
```
D. Save the data as **new.RData to your RStudio. Write the
R script.
```{r}
save(selcol, file = "new.RData")
```
E. Display the first six rows and last six rows of the
new.RData. What is the R script?
```{r}
load("new.RData")
head(selcol)
tail(selcol)
```
**10. Create a list of ten (10) vegetables you ate during your lifetime. If none, just list down.
A. Write the R scripts and its output.
```{r}
veg <- list("Kangkong", "Patatas", "Peas", "GreenPeas", "Carrot", "Kalabasa", "Tomato", "Mais", "Sibuyas", "Malunggay")
veg
```
B. Add 2 additional vegetables after the last vegetables
in the list. What is the R script and its output?
```{r}
veg <- append(veg, list("Upo", "Okra"))
veg
```
C. Add 4 additional vegetables after index 5. How many
datapoints does your vegetable list have? What is the
R script and its output?
```{r}
veg <- append(veg, list("Garlic", "Yam", "Repolyo", "Mushroom"), after = 5)
veg
```
D. Remove the vegetables in index 5, 10, and 15. How
many vegetables were left? Write the codes and its
output.
```{r}
veg <- veg[-c(5, 10, 15)]
veg
```


